Compositional equivalences based on Open pNets

### 2020-07-15 2016-Weak-FH-Bisim/WeakBisim.tex
small typos in appendix

$\forall \texttt{p-a1}. \{True \land \forall \texttt{m1}. \texttt{p-a1} \neq \texttt{p-send(m1)}\\
 \hspace{3mm} \implies \exists \texttt{pa-2}. 
(\texttt{p-a1} = \texttt{p-a2}
\land \forall \texttt{m2}. \texttt{p-a2} \neq \texttt{p-send(m2)}
\land \nounderline{\texttt{p-a1}} = \nounderline{\texttt{p-a2}} 
\land True\}$

\medskip That is trivially true, choosing \texttt{p-a1=p-a2} for each given \texttt{p-a1}.

@@

  \bigskip
  All others pairs from this set are just as easily proved true.

>>>>

$\forall \texttt{p-a1}. \{True \land \forall \texttt{m1}. \texttt{p-a1} \neq \texttt{p-send(m1)}\\
 \hspace{3mm} \implies \exists \texttt{p-a2}. 
(\texttt{p-a1} = \texttt{p-a2}
\land \forall \texttt{m2}. \texttt{p-a2} \neq \texttt{p-send(m2)}
\land \nounderline{\texttt{p-a1}} = \nounderline{\texttt{p-a2}} 
\land True\}$

\medskip That is trivially true, choosing \texttt{p-a2=p-a1} for each given \texttt{p-a1}.

@@

  \bigskip
  All others pairs from this set are just as easily proven true.
